Models

### 2023-02-14 analysis/05_model_metrics.Rmd
adapt for glm study model approach

study_slope_data <- study_slopes %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())

@@

#All model estimates in one dataframe
# slope_models <- bind_rows(duration_slope, startyear_slope)

>>>>

study_slope_data <- indv_mod_table %>%
  filter(term == "year_scaled") %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())

@@

#All model estimates in one dataframe
slope_models <- bind_rows(duration_slope, startyear_slope)
